Discrete Probability for Discrete Quantum Computing

### 2016-05-03 prob.tex
prob.tex \begin{example}[Dempster-Shafer Theory of Evidence] updates...

\begin{example}[Dempster-Shafer Theory of Evidence] We have five
  employees whose precise age is not known. All is given is a range for
  each employee:
\[\begin{array}{rcl}
\textrm{Age}(M_1) &\in& [22,26] \\
\textrm{Age}(M_2) &\in& [20,22] \\
\textrm{Age}(M_3) &\in& [30,35] \\
\textrm{Age}(M_4) &\in& [20,22] \\
\textrm{Age}(M_5) &\in& [28,30] 
\end{array}\]
What is the probability that an employee's age is in the range
$[20,25]$? Looking at the data, it is \emph{possible} for $M_1$'s age
to be within the range, it is \emph{not possible} for $M_3$'s age to
be within the range, and it is \emph{certain} or \emph{necessary} that
$M_4$'s age is in the range. Clearly saying that an event is
\emph{necessary} is equivalent to saying that its complement is
\emph{not possible}. Aggregating the results for the five employees,
we can calculate that is necessary that 2 employees have their ages
within the range, and it is possible that 3 employees have their ages
within the range. We express this formally as saying that the
probability of the event is $[0.4,0.6]$. Now consider another event
asking whether the ages are some other disjoint range
$[26,40]$. Reasoning in a similar way we calculate that the
probability for this event is $[0.4,0.6]$. Now let's take the two events
together and ask about the possibility of the ages to be in the range
$[20,40]$. Clearly that probability must be $[1,1]$ as every
employee's age is in that range. The way to calculate this probability
from the individual probabilities of the events is as follows: 
\begin{itemize}
\item \amr{can you try to fix this... perhaps it is not consistent
    with the interval-valued formalization but it is really nice if we
    can make it work}
\end{itemize}
\qed\end{example}

>>>>

\begin{example}[Dempster-Shafer Theory of Evidence] We have five
  employees whose precise age is not known. All is given is a range for
  each employee:
\[\begin{array}{rcl}
\textrm{Age}(M_{1}) & \in & [22,26]=D_{1}\\
\textrm{Age}(M_{2}) & \in & [20,22]=D_{2}\\
\textrm{Age}(M_{3}) & \in & [30,35]=D_{3}\\
\textrm{Age}(M_{4}) & \in & [20,22]=D_{4}\\
\textrm{Age}(M_{5}) & \in & [28,30]=D_{5}
\end{array}\]
What is the probability that an employee's age is in the range
$[20,25]$? Looking at the data, it is \emph{possible} for $M_1$'s age
to be within the range, it is \emph{not possible} for $M_3$'s age to
be within the range, and it is \emph{certain} or \emph{necessary} that
$M_4$'s age is in the range. Clearly saying that an event is
\emph{necessary} is equivalent to saying that its complement is
\emph{not possible}. Aggregating the results for the five employees,
we can calculate that is necessary that 2 employees have their ages
within the range, and it is possible that 3 employees have their ages
within the range. We express this formally as saying that the
probability of the event is $[0.4,0.6]$. Now consider another event
asking whether the ages are some other disjoint range
$[26,40]$. Reasoning in a similar way we calculate that the
probability for this event is $[0.4,0.6]$. Now let's take the two events
together and ask about the possibility of the ages to be in the range
$[20,40]$. Clearly that probability must be $[1,1]$ as every
employee's age is in that range. The way to calculate this probability
from the individual probabilities of the events is as follows: 
\begin{itemize}
\item \amr{can you try to fix this... perhaps it is not consistent
    with the interval-valued formalization but it is really nice if we
    can make it work}
\item Because ages are all integers, and we only consider ages from 20 to
40. Hence, the sample space~$\Omega$ can be $\left\{ 20,21,\ldots,39,40\right\} $,
and the set of events are $2^{\Omega}$ as usual.\\
\yutsung{I have numerically verified if we set $\Omega=\left\{ 20,22,25,26,28,30,35,40\right\} $,
and the answer should be the same as $\left\{ 20,21,\ldots,39,40\right\} $
because only end-points should matter in the question... I will numerically
verify $\left\{ 20,21,\ldots,39,40\right\} $, or prove they are the
same later...} 
\item Given a event~$E\subseteq\Omega$, the probability of $E$ can be
defined by 
\[
\pmeas(E)=\left[\frac{1}{5}\left|\left\{ i\middle|D_{i}\cap E\ne\emptyset\right\} \right|,\frac{1}{5}\left|\left\{ i\middle|D_{i}\subseteq E\right\} \right|\right]\textrm{ ,}
\]
where $\left|A\right|$ is the number of elements in $A$. Then, we
can verify that $\pmeas$ in an interval-value probability measure.
\end{itemize}
\qed\end{example}
